Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-08 journal paper/content/sec-theory.tex
Minor edit.
Added "prelims" subsections.

@@

\ascomment{need to polish this subsection}

@@

>>>>

\subsection{Preliminaries}
\label{sec:theory-prelims}

\ascomment{to be added / copied from the ITCS paper}

@@

\ascomment{TODO: revise this subsection.}

@@

\ascomment{TODO: arbitrary reward distributions.}
For each action $a\in A$ there is a parametric family $\psi_a(\cdot)$ of reward distributions, parameterized by the mean reward $\mu_a$. (The paradigmatic case is 0-1 rewards with a given expectation.) Whenever a given action $a\in A$ is chosen, the reward is drawn independently from distribution $\psi_a(\mu_a)$. The prior $\priorMu$ and the distributions $(\psi_a(\cdot)\colon a\in A)$ constitute the (full) Bayesian prior on rewards, denoted $\prior$.
